\documentclass[sigconf]{acmart}

\pagestyle{plain}
\usepackage{booktabs} % For formal tables
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{xcolor}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  language=C,
  basicstyle=\scriptsize\ttfamily,
  %basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=[1]\color{blue},       % keyword style
  keywordstyle=[2]\color{mymauve},       % keyword style
  morekeywords=[2]{*, },            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=1,                       % sets default tabsize to 2 spaces
  title=\lstname,                   % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=10pt,
}

% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


\begin{document}
\title{RambutanAcc: a Dataflow Runtime System for Accelerator-based Clusters}


%\author{
%Tan Nguyen,
%John Bachan,
%Bryce Lelbach,
%Sam Williams,
%John Shalf,
%David Donofrio, and Cy Chan\\
%Lawrence Berkeley National Laboratory, USA\\
%{\small \{tannguyen, jdbachan, balelbach, swwilliams, jshalf, ddonofrio, cychan\}@lbl.gov}}


\begin{abstract}
Recently heterogeneous node architectures have gained traction in HPC.
Systems equipped with accelerators each having thousands of cores are increasingly commonplace.
However, such architectural design results in many challenging problems.
For example, scaling a kernel to all the cores of an accelerator is not usually a trivial task.
In addition, masking communication overheads between the host and accelerator as well as among accelerators under useful computations requires an excessive amount of programming effort, and this optimization also complicates the application code.
In this paper, we present a task-based programming model that abstracts away many hardware details associated with sophisticated architectures such as GPUs.
We also develop a runtime system that can schedule fine-grained tasks on portions of an accelerator, increasing performance and scalability.
The runtime also hides communication costs automatically.
Experimental evaluations on 3 benchmarks representing different application motifs show significant performance gains at very modest programming cost.
These promising results can lead to special interests in the HPC community in tuning libraries such as cuSPARSE for co-running routines on a GPUs.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Hybrid Node - a Notable Design Trend}
\label{sec:motivation}
\input{motivation}

\section{Programming Model}
\label{sec:model}
\input{model}

\section{Implementation}
\label{sec:impl}
\input{impl}


\section{Experimental Results}
\label{sec:results}
\input{results}

\section{Related work}
\label{sec:related}
\input{related}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}


\section*{Acknowledgment}
All authors from LBNL were supported by the Office of Advanced Scientific Computing Research in the Department of Energy Office of Science under contract number DE-AC02-05CH11231.
RambutanAcc and application codes were developed on TiDA, a workstation housed at LBNL.
All GPUs on TiDA were provided by NVIDIA.
Experiments were conducted on Comet at SDSC.
We would like to thank Paul Hargrove for his great help on GASNet.
We also thank Yifeng Cui for time allocations on the Comet system.
Tan Nguyen was a fellow of the Vietnam Education Foundation while conducting this research.

\bibliographystyle{ACM-Reference-Format}
\bibliography{ref} 


\end{document}
